---
title: "MDL Multiresolution Regression Framework"
output: html_notebook
---
#To run the framework, please jump to "Code running block".


#Simple simulation -> 4 types of layers 

```{r}
#clsList<-cbind(100,10)
#stdList<-c(1,1.5)
#dumDim<-5

LinearSimFunc <- function(clsList,stdList,dumDim) {
  totalDim <-length(clsList) + dumDim
  totalRow <- sum(clsList)
  mat<- matrix( rnorm(totalRow*totalDim,mean=0,sd=1), totalRow, totalDim) 
  Y <-matrix(0, totalRow, 1)
  cls<-matrix(0, totalRow, 1)
  k<-1
  for(i in seq(1, length(clsList), by = 1) )
  {
    n<-clsList[i]
    const1<-runif(1, min=2, max=100)
    for( j in seq(k,k+n-1) )
    {
      cls[j] <-i
      Y[j]<- const1*mat[j,i]
    }
    k<-k+n
  }
  return(list("Y"=Y,"mat"=mat,"cls"=cls))
}


clusterSimpleGenT1Func <- function(indvN) {
  N<-indvN*8
  clsLayer<-matrix(1, N, 3)
  nL2<-indvN*2
  for (i in seq(1,4) ) # fill 2nd layer
  {
    st<-(i-1)*nL2+1
    fn<-i*nL2
    clsLayer[ st:fn, 2]<-i;
    
  }
  for (i in seq(1,8) ) # fill 3nd layer
  {
    st<-(i-1)*indvN+1
    fn<-i*indvN
    clsLayer[ st:fn, 3]<-i;
    
  }
  clsList<-cbind(N)
  stdList<-c(1)
  dumDim<-19
  out<- LinearSimFunc(clsList,stdList,dumDim)
  return(list("clsLayer"=clsLayer,"Y"=out$Y,"X"=out$mat,"cls"=out$cls))
}

clusterSimpleGenT2Func <- function(indvN) {
  N<-indvN*8
  clsLayer<-matrix(1, N, 3)
  nL2<-indvN*2
  for (i in seq(1,4) ) # fill 2nd layer
  {
    st<-(i-1)*nL2+1
    fn<-i*nL2
    clsLayer[ st:fn, 2]<-i;
    
  }
  for (i in seq(1,8) ) # fill 3nd layer
  {
    st<-(i-1)*indvN+1
    fn<-i*indvN
    clsLayer[ st:fn, 3]<-i;
    
  }
  clsList<-cbind(nL2,nL2,nL2,nL2)
  stdList<-c(1,1,1,1)
  dumDim<-16
  out<- LinearSimFunc(clsList,stdList,dumDim)
  return(list("clsLayer"=clsLayer,"Y"=out$Y,"X"=out$mat,"cls"=out$cls))
}

clusterSimpleGenT3Func <- function(indvN) {
  N<-indvN*8
  clsLayer<-matrix(1, N, 3)
  nL2<-indvN*2
  for (i in seq(1,4) ) # fill 2nd layer
  {
    st<-(i-1)*nL2+1
    fn<-i*nL2
    clsLayer[ st:fn, 2]<-i;
    
  }
  for (i in seq(1,8) ) # fill 3nd layer
  {
    st<-(i-1)*indvN+1
    fn<-i*indvN
    clsLayer[ st:fn, 3]<-i;
    
  }
  clsList<-cbind(indvN,indvN,indvN,indvN,indvN,indvN,indvN,indvN)
  stdList<-c(1,1,1,1,1,1,1,1)
  dumDim<-12
  out<- LinearSimFunc(clsList,stdList,dumDim)
  return(list("clsLayer"=clsLayer,"Y"=out$Y,"X"=out$mat,"cls"=out$cls))
}

clusterSimpleGenT4Func <- function(indvN) {
  Data1<-clusterSimpleGenT1Func(indvN)
  Data2<-clusterSimpleGenT2Func(indvN)
  Data3<-clusterSimpleGenT3Func(indvN)
  
  clsLayer<-rbind(Data1$clsLayer,Data2$clsLayer+10,Data3$clsLayer+20)
  rN<-dim(clsLayer)[1]
  clsLayer<-cbind(numeric(rN)+1,clsLayer)
  Y<-rbind(Data1$Y,Data2$Y,Data3$Y)
  X<-rbind(Data1$X,Data2$X,Data3$X)
  cls<-rbind(Data1$cls,Data2$cls+1,Data3$cls+5)
  return(list("clsLayer"=clsLayer,"Y"=Y,"X"=X,"cls"=cls))
}

```
END

# Mapping Cluster

```{r}
remappingClusterInx<-function(clsLayer)
{
  nL<- dim(clsLayer)[2]
  nIdv<-dim(clsLayer)[1]
  nclsLayer<-matrix(1, nIdv, nL)
  clsNameMappingTable<-list()
  for(i in seq(1,nL))
  {
    currLayer<-clsLayer[,i]
    currLayerList<-unique(currLayer)
    #print(sprintf("rmmfunc L%d",i) )
    #print(currLayerList)
    for( j in seq(1,length(currLayerList)))
    {
      targetInxvec <-currLayer== currLayerList[j]
      nclsLayer[targetInxvec,i] <-j
    }
    clsNameMappingTable[[i]]<-currLayerList
  }
  
  return(list("nclsLayer"=nclsLayer,"clsNameMappingTable"=clsNameMappingTable))
}
```




# Phase 1: training
```{r}
# setting
linearModelTraining<-function(DataT)
{
  
insigThs <- 1e-8
alpha<- 0.05
# ====================

out1<-remappingClusterInx(DataT$clsLayer)
DataT$clsLayer<-out1$nclsLayer
DataT$clsNameMappingTable<-out1$clsNameMappingTable
out<-dim(DataT$clsLayer)
N<-out[[1]]
nL<-out[[2]]
models<-list()
residualMat<-matrix(0,N,nL)
nNodes <-0
IDk<-1
for(inx in seq(1,nL))
{
  currLayer<- DataT$clsLayer[,inx]
  currLayerList<-unique(currLayer)
  nCls<- length( currLayerList )
  nNodes<-nNodes + nCls
  submodels<-list()
  for(inx2 in seq(1,nCls))
  {
    inxFilterVec<- currLayer == currLayerList[inx2]
    x<-DataT$X[inxFilterVec,]
    y<-DataT$Y[inxFilterVec,]
    df = data.frame(y, x)
    #===========================st Linear model
    submodels[[inx2]] <- lm(y ~ ., data = df)
    submodels[[inx2]] $ID<-IDk
    IDk<-IDk +1
    #===========================fn Linear model
    if(inx<nL)
      submodels[[inx2]]$ChildrenCls<- unique(DataT$clsLayer[inxFilterVec,inx+1])
    else
      submodels[[inx2]]$ChildrenCls<- NULL
    
    if(inx>1)
    {
      submodels[[inx2]]$ParentCls<- unique(DataT$clsLayer[inxFilterVec,inx-1])
    }
    else
      submodels[[inx2]]$ParentCls<- NULL
    
    submodels[[inx2]]$optFlag<-FALSE
    
    SelectedFeatures<- summary(submodels[[inx2]])$coefficients[,4] < alpha
    sigFeature<- abs(summary(submodels[[inx2]])$coefficient[,1])>insigThs
    
    SelectedFeatures<- SelectedFeatures & sigFeature 
    selFeatureSet<-1:length(SelectedFeatures)
    selFeatureSet<- selFeatureSet[SelectedFeatures]
    submodels[[inx2]]$selFeatureSet<-selFeatureSet
    
    if(length(y)>1)
      residualMat[inxFilterVec,inx] <- submodels[[inx2]]$residuals
    else
      residualMat[inxFilterVec,inx] <-sum(submodels[[inx2]]$residuals)
    
    submodels[[inx2]]$clsName<-sprintf("C%g",DataT$clsNameMappingTable[[inx]][[inx2]])
    print(sprintf("Layer%d,Cls:%s",inx,submodels[[inx2]]$clsName))
  }
  
  models[[inx]]<-submodels
}
  DataT$nNodes<-nNodes
  return(list("models"=models,"DataT"=DataT))
}
```

MDL
```{r}
realNumBits = 64
insigThs = 1
#============= NEW
getRealStoreBits<-function(realVec)
{
  # getRealStoreBits(realVec)$realVecBits
  normalizedRealVec<-realVec
  normalizedRealVec[abs(normalizedRealVec)==insigThs]<-2 # for val = 1 need 2 bits
  normalizedRealVec[abs(normalizedRealVec)<insigThs]<-1
  realVecBits <- sum( ceiling(log2(abs(normalizedRealVec)) )+1)
  return(list("realVecBits"=realVecBits))
}

getModelInfoRecRatio<-function(h1ResidualVec,h2ResidualVec,h1coeff,h2coeff)
{
  h1ResBits<-getRealStoreBits(h1ResidualVec)$realVecBits
  h2ResBits<-getRealStoreBits(h2ResidualVec)$realVecBits
  h1modelBits <- getRealStoreBits(h1coeff)$realVecBits
  h2modelBits <- getRealStoreBits(h2coeff)$realVecBits
  h1TotalBits <- (h1ResBits+h1modelBits )
  h2TotalBits <- (h2ResBits+h2modelBits )
  modelInfoRecBitsRatio<-(  h1TotalBits -  h2TotalBits )/h1TotalBits
  return(list("modelInfoRecRatio"=modelInfoRecBitsRatio,"h1ResBits"=h1ResBits,"h2ResBits"=h2ResBits,"h1modelBits"=h1modelBits,"h2modelBits"=h2modelBits))
}
```


Cross-validation part
```{r}
crossValEstFunc<-function(X,Y,clsInxVec)
{
  # X is a vector of independent vars, Y is a vector of a dependent var.
  # clsInxVec is a vector of clustering indices of rows in X and Y.
  # clsInxVec is always the local index vector!
  
  # return Coefficient of Determination R^2
  clsVec<-unique(clsInxVec)
  predY<-numeric(length(Y))
  
  #print(length(clsVec))
  for(cls in clsVec)
  {
    # cls is the validate cluster and the rest are training part
    currClsInx<-clsInxVec == cls
    currReverseClsInx <- !currClsInx # training
    
    #print(sprintf("Cls%d, Length%d",cls,sum(currClsInx)))
    
    x<-X[currReverseClsInx,]
    y<-Y[currReverseClsInx]
    
    df = data.frame(y, x)
    
    
    model1<- lm(y ~ ., data = df)
    
    if(sum(currClsInx)!=1)
    {
      predYtmp<-predict(model1, data.frame(X[currClsInx,]) )
    }
    else
      predYtmp<-0

    predY[currClsInx]<-predYtmp
  }
  return(list("r2"=cor(Y,predY)^2))
}

crossVal10FoldEstFunc<-function(X,Y)
{
  # X is a vector of independent vars, Y is a vector of a dependent var.
  # clsInxVec is a vector of clustering indices of rows in X and Y.
  # clsInxVec is always the local index vector!
  
  # return Coefficient of Determination R^2
  
  train.control <- trainControl(method = "cv", number = 10)

  x<-X
  y<-Y
  
  df = data.frame(y, x)
  
  
  model1 <- train(y ~., data = df, method = "lm",
             trControl = train.control)

  return(list("r2"=model1$results$Rsquared))
}
```


New Main
```{r}
library(caret)
FindMaxHomoPartition<-function(DataT,gamma)
{
minR2cv<-Inf
out<-dim(DataT$clsLayer)
N<-out[[1]]
nL<-out[[2]]
Vc <-cbind(numeric(N),numeric(N))
out<-linearModelTraining(DataT)
models<-out$models
DataT<-out$DataT

#options( warn = -1 )
for(k in seq(1,nL))
{
  
  nCls<-length(models[[k]]) # number of cluster in ith layer
  currLayerList<- unique(DataT$clsLayer[,k])
  cat("\014")
  for(j in seq(1,nCls)) 
  {
     
    inxFilterVec<-DataT$clsLayer[,k] == currLayerList[j] # selecting only members of jth cluster in ith layer
    H0coeff<-mean(DataT$Y[inxFilterVec],na.rm = TRUE)
    H0Residual<- DataT$Y[inxFilterVec]-H0coeff
    H1coeff<-models[[k]][[j]]$coefficients
    HlinResidual<-models[[k]][[j]]$residuals
    
    H0Residual[is.na(H0Residual)]<-0
    H1coeff[is.na(H1coeff)]<-0
    HlinResidual[is.na(HlinResidual)]<-0
    
    # positive modelInfoRecRatio  == H1 better than H0
    modelInfoRecRatio<- getModelInfoRecRatio(H0Residual,HlinResidual,H0coeff,H1coeff)$modelInfoRecRatio
    

    models[[k]][[j]]$modelInfoRecRatio<-modelInfoRecRatio # modelInfoRecRatio>0 mean better than H0
    if(min(Vc[inxFilterVec,1])==0 )
    {
      if(!is.null(models[[k]][[j]]$ChildrenCls))
      {
        HparentCoeff<-H1coeff
        HparentResidual<-HlinResidual
        HparentCoeff[is.na(HparentCoeff)]<-0
        HparentResidual[is.na(HparentResidual)]<-0
        
        
        HchildrenCoeff<-list()
        HchildrenResidual<-list()
        
        
        #======= cross-validation
        clsInxVec<-DataT$clsLayer[inxFilterVec,k+1]
        if(length(unique(clsInxVec))>1)
        {
          R2cv<-crossValEstFunc(DataT$X[inxFilterVec,],DataT$Y[inxFilterVec],clsInxVec)$r2
          
          for(chCls in models[[k]][[j]]$ChildrenCls)
          {
            HchildrenCoeff<-append(HchildrenCoeff,t(as.list(models[[k+1]][[chCls]]$coefficients)) )
            HchildrenResidual<-append(HchildrenResidual,as.list(models[[k+1]][[chCls]]$residuals) )
          }
          HchildrenCoeff<-as.numeric(HchildrenCoeff)
          HchildrenCoeff[is.na(HchildrenCoeff)]<-0
          
          HchildrenResidual<-as.numeric(HchildrenResidual)
          HchildrenResidual[is.na(HchildrenResidual)]<-0
          clustInfoRecRatio<- getModelInfoRecRatio(HchildrenResidual,HparentResidual,HchildrenCoeff,HparentCoeff)$modelInfoRecRatio
          models[[k]][[j]]$clustInfoRecRatio<-clustInfoRecRatio
        
        }else
        {
          R2cv<-0
          clustInfoRecRatio<-0
        }
#         print(sprintf("R2cv:%f",R2cv))
        models[[k]][[j]]$R2cv<-R2cv
        
        # end cross-validation
        
        
        if(clustInfoRecRatio >0 && R2cv>=gamma )
        {
          minR2cv<-min(c(minR2cv,R2cv))
          Vc[inxFilterVec,1] <- k
          Vc[inxFilterVec,2] <- j 
        }
    
      }else # No child
      {
        if(sum(inxFilterVec)>100)
        {
          R2cv<-crossVal10FoldEstFunc(DataT$X[inxFilterVec,],DataT$Y[inxFilterVec])$r2
        }
        else
        {
          R2cv<-0
        }
#         print(sprintf("R2cv:%f",R2cv))
        minR2cv<-min(c(minR2cv,R2cv))
        models[[k]][[j]]$R2cv<-R2cv
        Vc[inxFilterVec,1] <- k
        Vc[inxFilterVec,2] <- j
      }
      print(sprintf("Calculating Layer%d,Cls%d:modelInfoRecRatio %f, R2cv %f",k,j,modelInfoRecRatio,R2cv))
    }
  }
}

Copt<-unique(Vc)
M<-dim(Copt)[1]
Copt<-cbind(Copt,numeric(M),numeric(M))
for(j in seq(1,M))
{
  Copt[j,3] <- models[[Copt[j,1]]][[Copt[j,2]]]$modelInfoRecRatio
  Copt[j,4] <- models[[Copt[j,1]]][[Copt[j,2]]]$R2cv
}
cat("\014") 
print("========== List of Optimal Clusters ==========")
for(i in seq(1,M))
{
  clsName<-models[[Copt[i,1]]][[Copt[i,2]]]$clsName
  print(sprintf("Layer%d,ClS-%s:modelInfoRecRatio=%.2f, R2cv=%.2f",Copt[i,1],clsName,Copt[i,3],Copt[i,4]) )
}
print(sprintf("minR2cv:%f",minR2cv))
#print(Copt)
#options( warn = 1 )
return(list("Copt"=Copt,"models"=models,"minR2cv"=minR2cv,"DataT"=DataT) )
}

```
sss

#Experimental code 1: Greedy algorithm
```{r}
greedyAlgo<-function(DataT,out)
{
N<-length(DataT$Y)
flagVec<-logical(N)
nL<-dim(DataT$clsLayer)[2]
Vc <-cbind(numeric(N),numeric(N))
mSquareErr<-list()
sortVec<-list()
sortCls<-list()
l<-1
for(k in seq(1,nL) )
{
  currLayer<-unique(DataT$clsLayer[,k])
  layerMSquareErr<-list()
  for(j in seq(1,length(currLayer) ) )
  {
    sortVec[[l]]<-mean(out$models[[k]][[j]]$residuals^2)
    sortCls[[l]]<-c(j,k)
    l=l+1
  }
  
}
sortVec<-as.numeric(sortVec)
orderVec<-order(sortVec)

for(i in orderVec)
{
  currCls<-sortCls[[i]]
  mark<-unique(DataT$clsLayer[,currCls[2]])
  inxVec<-DataT$clsLayer[,currCls[2]] == mark[currCls[1] ]
  if(sum(flagVec[inxVec])==0)
  {
    flagVec[inxVec]<-TRUE
    k<-currCls[2] # Layer
    j<-currCls[1] # Cls in Layer
    Vc[inxVec,1]<-k
    Vc[inxVec,2]<-j
    
    print(sprintf("Greedy: Layer%d, cls%d",k,j) )
    if(is.null(out$models[[k]][[j]]$R2cv))
    {
      inxFilterVec<-DataT$clsLayer[,k] == j # selecting only members of jth cluster in ith layer
      out$models[[k]][[j]]$R2cv<- crossVal10FoldEstFunc(DataT$X[inxFilterVec,],DataT$Y[inxFilterVec])$r2
    }
  }
}
CoptGreedy<-unique(Vc)
return(list("Copt"=CoptGreedy,"out"=out))
}
```

#Evaluation parts
```{r}
# support function
getResidualFromCopt<-function(Copt,models)
{
  M<-dim(Copt)[1]
  residuals<-list()
  for(i in seq(1,M))
  {
    residuals<-append(residuals,models[[Copt[i,1]]][[Copt[i,2]]]$residuals)
  }
  return(list("residuals"=as.numeric(residuals) ) )
}
getPartitionFscore<-function(TrueCopt,Copt,clsLayer)
{
  # TrueCopt[k,j] 

  TrueCopt<-matrix(TrueCopt,ncol=2)
  #Copt<-matrix(Copt,ncol=4)
  N1<-dim(TrueCopt)[1]
  N2<-dim(Copt)[1]
  TrueFlag<-logical(N1)
  PredFlag<-logical(N2)
  Fscore<-0
  TP<-0
  FP<-0
  FN<-0
  
  for(i1 in seq(1,N1))
  {
    currTrCls<-TrueCopt[i1,1:2]
    for(i2 in seq(1,N2))
    {
      currPdCls<-Copt[i2,1:2]
      if( sum(currTrCls ==currPdCls) ==2 ) # true cls is in pred cls set
      {
        TrueFlag[i1] = TRUE
        PredFlag[i2] = TRUE
        break
      }
    }
  }
  # Find true positive and false negative
  for(i1 in seq(1,N1))
  {
    currTrCls<-TrueCopt[i1,1:2]
    if(TrueFlag[i1]==TRUE)
    {
      TP<-TP+ sum(clsLayer[,currTrCls[1]] == currTrCls[2])
    }
    else
    {
      FN<-FN+ sum(clsLayer[,currTrCls[1]] == currTrCls[2]) 
    }
  }
  # Find  false positive
  for(i2 in seq(1,N2))
  {
    currPdCls<-Copt[i2,1:2]
   # print(currPdCls)
    if(PredFlag[i2]==FALSE)
    {
      FP<-FP+ sum(clsLayer[,currPdCls[1]] == currPdCls[2])
    }
  }
  
  prcVal<-TP/(TP+FP)
  recall<-TP/(TP+FN)
  Fscore<-2*(prcVal*recall)/(recall+prcVal)
  return(list("prcVal"=prcVal,"recall"=recall,"Fscore"=Fscore))
}

```

#Code running block: the framework execution chunk starts here!
instruction
- Please run all chunks above (Ctrl+Alt+P)
- Then set the parameter below (Input: DataT and gamma)
- Run all chunks below to start the framwork

Explanation: FindMaxHomoPartition(DataT,gamma)
- INPUT: DataT$X[i,j] is the value of jth independent variable of ith individual. 
- INPUT: DataT$Y[i] is the value of dependent variable of ith individual. 
- INPUT: DataT$clsLayer[i,k] is the cluster label of ith individual in kth cluster layer.

- OUTPUT: Copt[p,1] is equal to k means a cluster that is a pth member of the maximal homogeneous partition is at kth layer and the cluster name in kth layer is Copt[p,2]
- OUTPUT: Copt[p,3] is "Model Information Reduction Ratio" of pth member of the maximal homogeneous partition: positive means the linear model is better than the null model.
- OUTPUT: Copt[p,4] is $$R^2(C)_{\text{cv}}$$  of pth member of the maximal homogeneous partition. The greater Copt[p,4], the higher homoheneous degree of this cluster.
- OUTPUT: models[[k]][[j]] is the linear regression model of jth cluster in kth layer.
- OUTPUT: models[[k]][[j]]$clustInfoRecRatio is the "Cluster Information Reduction Ratio" between the jth cluster in kth layer and its children clusters in (k+1)th layer: positive means current cluster is better than its children clusters. Hence, we should keep this cluster at the member of maximal homogeneous partition instead of its children. 
```{r}
#========= Test 

# DataT<-clusterSimpleGenT1Func(10000)
# DataT<-clusterSimpleGenT2Func(10000)
# DataT<-clusterSimpleGenT3Func(10000)
DataT<-clusterSimpleGenT4Func(10000) # Type of simulation datasets

gamma <- 0.05 # Gamma parameter

out<-FindMaxHomoPartition(DataT,gamma)
out2<-greedyAlgo(out$DataT,out)
CoptGreedy<-out2$Copt
out<-out2$out

OPTresiduals<-getResidualFromCopt(out$Copt,out$models)$residuals
GreedyResiduals<-getResidualFromCopt(CoptGreedy,out$models)$residuals
RegResiduals<-out$models[[1]][[1]]$residuals
H0Residuals<-DataT$Y - mean(DataT$Y)
cat("\014") 
print(sprintf("OPT Residuals: RMSE=%g",sqrt(mean(OPTresiduals^2)) ))
print(sprintf("Greedy Residuals: RMSE=%g",sqrt(mean(GreedyResiduals^2)) ))
print(sprintf("Reg Residuals: RMSE=%g",sqrt(mean(RegResiduals^2)) ))
print(sprintf("\bar{Y} Residuals: RMSE=%g",sqrt(mean(H0Residuals^2)) ))
#FscoreOut<-getPartitionFscore(DataT$GrTHCopt,out$Copt,DataT$clsLayer)
```

TEST: iGraph output distplay
```{r}
library(igraph)
adjMat<- matrix(0,out$DataT$nNodes,out$DataT$nNodes)
nameList<-list()
graphOPTflag<-logical()


mainCOPT<-out$Copt
nL<-length(out$models)
k<-1
optCount<-0




for(i in seq(1,nL)) # ith Layer
{
  
  # =============
  flag1<-FALSE
  if( is.element(i,mainCOPT[,1] ) ) # this layer contains opt?
  {
    inxVec<-mainCOPT[,1] == i
    flag1<-TRUE

  }
  currLayer<- out$DataT$clsLayer[,i]
  nCls<-length(unique(currLayer) )

  for(j in seq(1,nCls)) # Nodes in ith layer
  {
    if(i>1) # build a graph
    {
      cID<-out$models[[i]][[j]]$ID
      parentCls<-out$models[[i]][[j]]$ParentCls
      pID<-out$models[[i-1]][[parentCls]]$ID
      adjMat[cID,pID]<- 1
      i
    }

    nameList[k]<-sprintf("L%dC%g",i,out$DataT$clsNameMappingTable[[i]][[j]])

    if( flag1 )
    {
      
      if(is.element(j,mainCOPT[inxVec,2])) # if found opt
      {
        graphOPTflag[k]<-TRUE

        optCount<-optCount+1
      }
      else
        graphOPTflag[k]<-FALSE
    }
    else
      graphOPTflag[k]<-FALSE
    k<-k+1
  }
}


g1 <- graph_from_adjacency_matrix( adjMat   ) %>%
  set_vertex_attr("label", value = nameList)


V(g1)$color <- ifelse(graphOPTflag == TRUE, "red", "gray")

#set_vertex_attr(g1,"label", value = nameList)
V(g1)$label.cex = 0.8
plot(g1, layout =  layout.auto,edge.arrow.size=0.25,vertex.label.color = "black")
```
#Mixture Model

```{r}
library("flexmix")
#DataT<-clusterSimpleGenT4Func(10000)
x<-DataT$X
y<-DataT$Y
df<- data.frame(y,x)
m2<-flexmix(y~.,data = df, k=4, control = list(minprior=0.2) )
predict(m2, data.frame( t(x[1,]) ) )
y[1]




```
# Exp mixture model - as baseline method
```{r}
library("flexmix")
DataT<-clusterSimpleGenT4Func(10000)
x<-DataT$X
y<-DataT$Y
getRMSEFromMixtureModel<-function(x,y,k)
{
  df<- data.frame(y,x)
  N<-length(y)
  df<- data.frame(y,x)
  mixmodel<-flexmix(y~.,data = df, k=k, control = list(minprior=0.02) )
  yh<-predict(mixmodel, data.frame( (x) ) )
  clsVec<-mixmodel@cluster
  residuals<-list()
  for(i in seq(1,N))
  {
    cls<-clsVec[i]
    currResidual<- y[i] - yh[[cls]][i]
    residuals<-append(residuals,currResidual)
  }
  RMSE<-sqrt(mean(as.numeric(residuals)^2))
  return(list("clsVec"=clsVec, "RMSE"=RMSE) )
}

#mixOut<-getRMSEFromMixtureModel(x,y,k=4)
#TrueClsVec<-DataT$cls
#PredClsVec<-mixOut$clsVec
getMixturePartitionFscore<-function(TrueClsVec,PredClsVec)
{
  # TrueCopt[k,j] 

  TrueclsMembers<-unique(TrueClsVec)
  M<-length(TrueclsMembers)
  Fscore<-0
  TP<-0
  FP<-0
  FN<-0
  for(trueCls in TrueclsMembers)
  {
    inxVec<-TrueClsVec == trueCls
    predCls<-median(PredClsVec[inxVec])
    predInxVec<- PredClsVec == predCls
    TP<- sum( predInxVec & inxVec) 
    FP<- sum( predInxVec & ! inxVec) 
    FN<- sum( !predInxVec & inxVec)
  }
   prcVal<-TP/(TP+FP)
  recall<-TP/(TP+FN)
  Fscore<-2*(prcVal*recall)/(recall+prcVal)
  return(list("prcVal"=prcVal,"recall"=recall,"Fscore"=Fscore) )
}
#mixOut<-getRMSEFromMixtureModel(x,y,k=13)
#getMixturePartitionFscore(DataT$cls,mixOut$clsVec)$Fscore
```
#Exp 100 mixture model 
```{r}
#ResOut<-list()
# for(i in seq(1,100))
# {
#   
#   DataT<-clusterSimpleGenT1Func(10000)
#   x<-DataT$X
#   y<-DataT$Y
#   mixOut<-getRMSEFromMixtureModel(x,y,k=1)
#   
#   ResOut$S1RMSE[[i]]<-mixOut$RMSE
#   outMX<-getMixturePartitionFscore(DataT$cls,mixOut$clsVec)
#   ResOut$S1Fscore[[i]]<-outMX$Fscore
#   ResOut$S1pre[[i]]<-outMX$prcVal
#   ResOut$S1rec[[i]]<-outMX$recall
#   print(sprintf("Type1 #%d",i) )
#   
# }
# print("Type1 Fin")
# cat("\014") 
# for(i in seq(1,100))
# {
# 
#   DataT<-clusterSimpleGenT2Func(10000)
#   x<-DataT$X
#   y<-DataT$Y
#   mixOut<-getRMSEFromMixtureModel(x,y,k=4)
# 
#   ResOut$S2RMSE[[i]]<-mixOut$RMSE
#   outMX<-getMixturePartitionFscore(DataT$cls,mixOut$clsVec)
#   ResOut$S2Fscore[[i]]<-outMX$Fscore
#   ResOut$S2pre[[i]]<-outMX$prcVal
#   ResOut$S2rec[[i]]<-outMX$recall
#   print(sprintf("Type2 #%d",i) )
# }
# print("Type2 Fin")
# cat("\014")

for(i in seq(1,100))
{

  DataT<-clusterSimpleGenT3Func(10000)
  x<-DataT$X
  y<-DataT$Y
  mixOut<-getRMSEFromMixtureModel(x,y,k=8)

  ResOut$S3RMSE[[i]]<-mixOut$RMSE
  outMX<-getMixturePartitionFscore(DataT$cls,mixOut$clsVec)
  ResOut$S3Fscore[[i]]<-outMX$Fscore
  ResOut$S3pre[[i]]<-outMX$prcVal
  ResOut$S3rec[[i]]<-outMX$recall
  print(sprintf("Type3 #%d",i) )
}
print("Type3 Fin")
cat("\014")

for(i in seq(1,100))
{
  DataT<-clusterSimpleGenT4Func(10000)
  mixOut<-getRMSEFromMixtureModel(x,y,k=13)
  x<-DataT$X
  y<-DataT$Y
  ResOut$S4RMSE[[i]]<-mixOut$RMSE
  outMX<-getMixturePartitionFscore(DataT$cls,mixOut$clsVec)
  ResOut$S4Fscore[[i]]<-outMX$Fscore
  ResOut$S4pre[[i]]<-outMX$prcVal
  ResOut$S4rec[[i]]<-outMX$recall
  print(sprintf("Type4 #%d",i) )
}
print("Type4 Fin")
cat("\014")
save(ResOut,file = "mixResout.rdata")
```

#Exp cal model Info.
```{r}
# support function
Copt<-out$Copt
models<-out$models
clsLayer<-DataT$clsLayer
#getclustInfoRecRatioFromCopt<-function(Copt,models,clsLayer)
{
  clsLayer<-remappingClusterInx(DataT$clsLayer)$nclsLayer
  M<-dim(Copt)[1]
  L<-length(models)

  residuals<-list()
  optR2cvList<-numeric(M)
  underR2cvList<-numeric(0)
  overR2cvList<-numeric(0)
  for(i in seq(1,M))
  {
    k<-Copt[i,1]
    j<-Copt[i,2]

    inxVex<-clsLayer[,k] == j # selecting only members of jth cluster in ith layer
      tmp<- crossVal10FoldEstFunc(DataT$X[inxVex,],DataT$Y[inxVex])$r2
    optR2cvList[i]<-tmp
    print(sprintf("j%d,k%d",j,k))
    if(k>1)
    {
      for(nK in seq(1,k-1))
      {
         
        parList<-unique(clsLayer[inxVex,nK])
        for(nJ in parList)
        {
          print(sprintf("Under-nJ-%d,nK-%d",nJ,nK))
          inxFilterVec<-clsLayer[,nK] == nJ # selecting only members of jth cluster in ith layer
      tmp<- crossVal10FoldEstFunc(DataT$X[inxFilterVec,],DataT$Y[inxFilterVec])$r2
          underR2cvList<-cbind(underR2cvList,tmp)
        }
      }
    }
    if(k<L)
    {
      for(nK in seq(k+1,L))
      {
        parList<-unique(clsLayer[inxVex,nK])
        for(nJ in parList)
        {
          print(sprintf("over nK-%d,nJ-%d",nK,nJ) )

          inxFilterVec<-clsLayer[,nK] == nJ # selecting only members of jth cluster in ith layer
      tmp<- crossVal10FoldEstFunc(DataT$X[inxFilterVec,],DataT$Y[inxFilterVec])$r2
          overR2cvList<-cbind(overR2cvList,tmp)
        }
        
      }
      
    }
    print("Fin")
  }
 # return(list("overclustInfoRecRatioList"=overclustInfoRecRatioList,"underclustInfoRecRatioList"=underclustInfoRecRatioList,  "optclustInfoRecRatioList"=optclustInfoRecRatioList) )
}

#out3<-getclustInfoRecRatioFromCopt(out$Copt,out$models,DataT$clsLayer)
```

#Real-data section
```{r}
 load("~/R/TestProject/Prov40DataPOP353K.RData")
 DataT<-DataTProv40
 gamma <- 0.05 # Gamma parameter
out<-FindMaxHomoPartition(DataT,gamma)
```

#box plot
```{r}
n1<-length(underR2cvList)
n2<-length(optR2cvList)
n3<-length(overR2cvList)
n<-n1+n2+n3
mat <- cbind(underR2cvList,optR2cvList,overR2cvList)
df <- data.frame(values = mat[1:n],  vars = rep(c("Underfitting","OPT","Overfitting"), times = c(n1,n2,n3)))
boxplot(values ~ vars, data = df,main = "Homogeneneity degree of clusters",  xlab = "Cluster Type", ylab = "R2cv")
```


#Evaluation with 100 datasets per each type
```{r}
#load("~/R/TestProject/OneHundredData.RData")
ResOut<-list()
gamma <- 0.5
k=1
for(i in seq(1,100))
{
  
  DataT<-DataS1[[i]]
  
  out<-FindMaxHomoPartition(DataT,gamma)
  SCoptGreedy<-greedyAlgo(DataT,out)$Copt
  
  ResOut$S1OPTresiduals[[i]]<-getResidualFromCopt(out$Copt,out$models)$residuals
  ResOut$S1GreedyResiduals[[i]]<-getResidualFromCopt(SCoptGreedy,out$models)$residuals
  ResOut$S1RegResiduals[[i]]<-out$models[[1]][[1]]$residuals
  ResOut$S1H0Residuals[[i]] <-DataT$Y - mean(DataT$Y)
  ResOut$S1GreedyFscoreOut[[i]]<-getPartitionFscore( DataT1$GrTHCopt,SCoptGreedy,DataT$clsLayer)
  ResOut$S1ourFscoreOut[[i]]<-getPartitionFscore( DataT1$GrTHCopt,out$Copt,DataT$clsLayer)
}
print("Type1 Fin")
k=2
for(i in seq(1,100))
{
  DataT<-DataS2[[i]]
  
  out<-FindMaxHomoPartition(DataT,gamma)
  SCoptGreedy<-greedyAlgo(DataT,out)$Copt
  
  ResOut$S2OPTresiduals[[i]]<-getResidualFromCopt(out$Copt,out$models)$residuals
  ResOut$S2GreedyResiduals[[i]]<-getResidualFromCopt(SCoptGreedy,out$models)$residuals
  ResOut$S2RegResiduals[[i]]<-out$models[[1]][[1]]$residuals
  ResOut$S2H0Residuals[[i]] <-DataT$Y - mean(DataT$Y)
  ResOut$S2GreedyFscoreOut[[i]]<-getPartitionFscore( DataT2$GrTHCopt,SCoptGreedy,DataT$clsLayer)
  ResOut$S2ourFscoreOut[[i]]<-getPartitionFscore( DataT2$GrTHCopt,out$Copt,DataT$clsLayer)
}
print("Type2 Fin")
k=3
for(i in seq(1,100))
{
  DataT<-DataS3[[i]]
  
  out<-FindMaxHomoPartition(DataT,gamma)
  SCoptGreedy<-greedyAlgo(DataT,out)$Copt
  
  ResOut$S3OPTresiduals[[i]]<-getResidualFromCopt(out$Copt,out$models)$residuals
  ResOut$S3GreedyResiduals[[i]]<-getResidualFromCopt(SCoptGreedy,out$models)$residuals
  ResOut$S3RegResiduals[[i]]<-out$models[[1]][[1]]$residuals
  ResOut$S3H0Residuals[[i]] <-DataT$Y - mean(DataT$Y)
  ResOut$S3GreedyFscoreOut[[i]]<-getPartitionFscore( DataT3$GrTHCopt,SCoptGreedy,DataT$clsLayer)
  ResOut$S3ourFscoreOut[[i]]<-getPartitionFscore( DataT3$GrTHCopt,out$Copt,DataT$clsLayer)
}
print("Type3 Fin")
k=4
for(i in seq(1,100))
{
  DataT<-DataS4[[i]]
  
  out<-FindMaxHomoPartition(DataT,gamma)
  SCoptGreedy<-greedyAlgo(DataT,out)$Copt
  
  ResOut$S4OPTresiduals[[i]]<-getResidualFromCopt(out$Copt,out$models)$residuals
  ResOut$S4GreedyResiduals[[i]]<-getResidualFromCopt(SCoptGreedy,out$models)$residuals
  ResOut$S4RegResiduals[[i]]<-out$models[[1]][[1]]$residuals
  ResOut$S4H0Residuals[[i]] <-DataT$Y - mean(DataT$Y)
  ResOut$S4GreedyFscoreOut[[i]]<-getPartitionFscore( DataT4$GrTHCopt,SCoptGreedy,DataT$clsLayer)
  ResOut$S4ourFscoreOut[[i]]<-getPartitionFscore( DataT4$GrTHCopt,out$Copt,DataT$clsLayer)
}
print("Type4 Fin")
k=5
save(ResOut,file="resOutData.RData")
```
Test